---
title: "Report-hormone-analysis"
author: "tmuylder"
date: "11/4/2020"
output:
  html_document: default
---


# Analysis of file hormone.csv #

This script analyzes the dataset of the hormone experiment performed on 01/01/2020. 
It contains the statistical analysis and plotting of figure 2D of the paper. 
Here is another sentence

## 1. Import libraries

If not already installed, install the packages by uncommenting following line)

```{r, warning=FALSE}
library(ggplot2)
```

## 2. Data analysis
### 2.1 Import samples

Import dataset with proper name handling & rename third column. 

```{r, results='hide'}
hormone <- read.csv2("data/20201102-hormone.csv")
names(hormone)[3] <- "Concentration"
hormone
```

```{r}
summary(hormone)
```

### 2.2 Create figures

Create plot effect of drug A and B on concentration of substance X measured in blood of patients. 

```{r fig_hormone, fig.cap="Result of drug on hormone concentration", fig.width=8, fig.height=4}
ggplot(hormone, aes(Drug,Concentration)) +
  stat_summary(fun=mean, geom="bar") +
  stat_summary(fun.data=mean_cl_normal, geom="errorbar", width=0.25) + geom_point() +
  coord_flip()
```

## 3. Discussion
There is a clear influence of the choice of drugs on the concentration of hormones present in patients blood. 

## 4. Conclusion 


## 5. Final notes

This report was created with built with `r getRversion()`. The following packages were used for the analysis

```{r}
sessionInfo()
```
